---
title: "Suspicious Cases in Brazilian MoS Data"
author: "James Hunter, PhD, EPM, UNIFESP"
date: '`r format(Sys.Date(), "%d %B %Y")`'
output: 
  html_document:
    theme: flatly
    df_print: paged
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
options(knitr.table.format = "html") 
knitr::knit_hooks$set(mysize = function(before, options, envir) {
  if (before) 
    return(options$size)
})
options(scipen = 10)
pacman::p_load(scales, tidyverse, lubridate, glue, here, ggpubr, 
               ggsci, janitor, summarytools, knitr, kableExtra, 
               data.table, patchwork)

```

## Records with Negative `cases_new` and `deaths_new`

Take each of the June Ministry of Health files, identify the records that have negative values for `cases_new` and `deaths_new` in each of the 9 files downloaded as of June 23rd, test the consistency of these values. 

Steps in the Process: 

1.    Build a data frame of these negative value records
2.    Make them sortable by which file they came from.
3.    Include date, state, population variables, the latter because this too appeared to be a way to keep cases out of the totals.

## Function to read in files to `br_data`  data table

```{r f_read_file}
read_rds <- function(file_date) {
  file_name <- here(glue("data/br_data_", file_date, ".rds"))
  df <- readRDS(file_name)
  return(df)
}
```


## Function to focus `br_data` only on those cases with negative values for `cases_new` or `deaths_new`

```{r f_negative_cases}
neg_vals <- function(br_data) {
  neg_mins <- br_data %>% 
    filter((cases_new < 0 | deaths_new < 0) & (mun == "" | (st == "SP" & mun != ""))) %>% 
    select(reg, st, state_name, mun, date, cases_new, deaths_new)
  glimpse(neg_mins)
  return(neg_mins)
}
```

## Set up tibbles `neg_records` to hold records across various files `neg_summary` for summaries of values by MoS file.

```{r setup_dfs}
neg_records <- tibble(file_day = character(),
                      st = character(),
                      mun = character(),
                      date = character(),
                      cases_new = integer(),
                      deaths_new = integer())

neg_summary <- tibble(file_day = character(),
                      tot_neg_records = integer(),
                      neg_cases_new = integer(),
                      neg_deaths_new = integer())

```

## Put negative records from `neg_mins` into `neg_records` and update summary: `neg_summary`

```{r f_neg_recs}

neg_recs <- function(file_date, neg_mins){
  tmp <- tibble(st = neg_mins$st,
                mun = neg_mins$mun,
                date = neg_mins$date,
                cases_new = neg_mins$cases_new,
                deaths_new = neg_mins$deaths_new)
  tmp$file_day <- file_date
  return(tmp)
}

neg_records <- rbind(neg_records, neg_recs(file_date, neg_mins))

neg_tots <- neg_mins %>% 
  summarise(neg_cases_new = sum(cases_new < 0),
            neg_deaths_new = sum(deaths_new < 0))

neg_summary <- neg_summary %>% 
  add_case(file_day = file_date,
           tot_neg_records = nrow(neg_mins),
           neg_cases_new = as.integer(neg_tots$neg_cases_new),
           neg_deaths_new = as.integer(neg_tots$neg_deaths_new))
```

## Set up `for` loop to process the files available

```{r loop}
file_dates <- c("2020-06-09",
                "2020-06-10",
                "2020-06-11",
                "2020-06-16",
                "2020-06-17",
                "2020-06-18",
                "2020-06-20",
                "2020-06-21",
                "2020-06-22")

neg_records <- tibble(file_day = character(),
                      st = character(),
                      mun = character(),
                      date = character(),
                      cases_new = integer(),
                      deaths_new = integer())

neg_summary <- tibble(file_day = character(),
                      tot_neg_records = integer(),
                      neg_cases_new = integer(),
                      neg_deaths_new = integer())

for (i in seq_along(file_dates)) {
  
  br_data <- read_rds(file_dates[i])
  neg_mins <- neg_vals(br_data)
  neg_records <- rbind(neg_records, neg_recs(file_dates[i], neg_mins))

  neg_tots <- neg_mins %>% 
    summarise(neg_cases_new = sum(cases_new < 0),
              neg_deaths_new = sum(deaths_new < 0))

  neg_summary <- neg_summary %>% 
    add_case(file_day = file_dates[i],
           tot_neg_records = nrow(neg_mins),
           neg_cases_new = as.integer(neg_tots$neg_cases_new),
           neg_deaths_new = as.integer(neg_tots$neg_deaths_new))
  
}

saveRDS(neg_records, here("data/June_neg_records.rds"))

```

